Macro Impacts

### 2016-08-12 Macro Impacts Revised.tex
further update
Final??? Code uploaded

When$kr\ll 1$, we have

@@

@@

U = \int_0^\infty \f{\diff k}{(2\pi)^2} k^2\abs{U(k)} = \f{1}{2\pi\sqrt{2\rho v_p^2}}\int_0^\infty\diff k\sqrt{\td{E_k}{k}{}}\,.

@@

In our case, when we want to only consider modes up to some $k_0$, we have

@@

U_k =  \f{1}{2\pi\sqrt{2\rho v_p^2}}\int_0^k\diff k'\sqrt{\td{E_k'}{k'}{}}

@@

\td{E_k'}{k'}{} = 2 C_1 k'e^{-k v_p\f{T}{Q}}\,,

@@

whence

@@

U_k &=  \f{\sqrt{C_1}}{2\pi\sqrt{\rho v_p^2}}\int_0^k\diff k' \sqrt{k'}e^{-\f{k v_p}{2}\f{T}{Q}}\,,\\

@@

&=\f{1}{2\pi kv_p}\sqrt{\f{E_{\te{ray}}}{\rho}}\f{Q}{v_p T}\p{\sqrt{2\pi}\sqrt{ \f{Q}{v_p T}}\te{Erf}\ps{\sqrt{\f{k v_p T}{2 Q}}} -2\sqrt{k} e^{-\f{k v_p T}{2 Q}}}\,,\\

>>>>

When $kr\ll 1$, we have

@@

The requirement that $kr\ll 1$ may determine the maximum size of the pixels. Then

@@

u \leq \int_0^\infty \f{\diff k}{(2\pi)^2} k^2\abs{U(k)} = \f{1}{2\pi\sqrt{2\rho v_p^2}}\int_0^\infty\diff k\sqrt{\td{E_k}{k}{}}\,.

@@

In our case, when we want to only consider modes up to some $k$, we have

@@

u_k \leq \f{1}{2\pi\sqrt{2\rho v_p^2}}\int_0^k\diff k'\sqrt{\td{E_k'}{k'}{}}

@@

\td{E_k'}{k'}{} = 2 C_1 k'e^{-k' v_p\f{T}{Q}}\,,

@@

whence, the maximum amplitude in the vicinity of the ray impact is

@@

u &\leq \f{\sqrt{C_1}}{2\pi\sqrt{\rho v_p^2}}\int_0^k\diff k' \sqrt{k'}e^{-\f{k v_p}{2}\f{T}{Q}}\,,\\

@@

&=\f{1}{2\pi kv_p}\sqrt{\f{E_{\te{ray}}}{\rho}}\f{Q}{v_p T}\p{\sqrt{2\pi}\sqrt{ \f{Q}{v_p T}}\te{Erf}\ps{\sqrt{\f{k v_p T}{2 Q}}} -2\sqrt{k} e^{-\f{k v_p T}{2 Q}}}\,.
This equation tells us the maximum displacement within the healpix pixel. Note that this is not a function of the area of the pixel. This is reasonable because the energy distribution is not a function of our partition of the sphere.
\section{Double Thought Out}
Thanks to Josh for a very useful conversation in helping to deduce what follows:
A key problem we are encountering is what follows. Suppose we shoot out a large number of rays that uniformly hit the surface of the sphere. If we have $N$ rays in a pixel, and then halve the area of the pixel, we will have $N/2$ rays in the pixel. This, in turn, reduces the energy in the pixel, and if not accounted for properly, the measured displacement. If, however, when increase the number of pixels, we also multiply the energy in each pixel by the number of pixels, then assuming a uniform distribution of rays, the average displacement across pixels does not change as the number of pixels increases.
Thus, suppose we have $M$ rays and $N$ pixels. Let $M_j$ be the number of rays incident on pixel $j$. Let $E_k^{ij}$ be the energy of the $i$th ray incident on the $j$th pixel. We then calculate
E_k^j =N\sum_{i=1}^{M_j}E_k^{ij}\,.
We now calculate the displacement, where $C_2^{ij} = v_p \f{T^{ij}}{Q^{ij}}$.
\td{E_k^{j}}{k}{} = N\sum_{i = 1}^{M_j}2 C_1^{ij} k'e^{-C_2^{ij} k}\,.
The integral would be impossible without an approximation
\sqrt{\td{E_k^{j}}{k}{}} & = \sqrt{N\sum_{i = 1}^{M_j}2 C_1^{ij} k'e^{-C_2^{ij} k}}\,,\\
& \leq \sqrt{N\p{\sum_{i = 1}^{M_j}\sqrt{2 C_1^{ij} k'e^{-C_2^{ij} k}}}^2}\,,\\
&=\sqrt{N}\sum_{i = 1}^{M_j}2 C_1^{ij} \sqrt{k'}e^{-C_2^{ij}\f{k}{2}}\,.
u_k^j&\leq\f{\sqrt{N}}{2\pi kv_p\sqrt{\rho}}\sum_{i}^{M_j}\f{\sqrt{E_k^{ij}}}{C_2^{ij}}\p{\sqrt{ \f{2\pi}{C_2^{ij}}}\te{Erf}\ps{\sqrt{\f{k}{2}C_2^{ij}}} -2\sqrt{k} e^{-\f{k }{2}C_2^{ij}}}\,.
